%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.6in,top=0.6in,right=0.5in,bottom=0.6in]{geometry} % Document margins

\name{Yosua Saputra} % Your name
\address{yosua.jsaputra@gmail.com $\vert$  626-940-6974 $\vert$ Alhambra, CA 91801 $\vert$  Github.com/ohayosua}

\begin{document}

%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Languages/Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }

Computer Languages: & $\bullet$ Python(eg. Numpy, Pandas, Matplotlib), \\
                    & $\bullet$ SQL(MySQL), \\
                    & $\bullet$ R(Tidyverse: tidyr $\&$ dplyr, ggplot2) \\
                 
Software Tools: & {$\bullet$} Jupyter Notebook, Overleaf, Microsoft Excel, Wix  \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	ACADEMIC PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic/Self Projects}


\begin{rSubsection}{Data Analysis Report}{\em August 2021}{Student's Exam Scores Analysis}{}
\item Demonstrated fundamentals in pandas and implemented various data manipulation operations for data set containing 1,000 students.
\item Manipulated and analyzed data set to devise questions for possibilities into improving exam scores.
\item Utilized matplotlib and constructed visualizations to compare specific groups of selected students associated with parental education and correlation between academic subjects
\item $\textbf{Link:}$
\url{https://github.com/ohayosua/Projects/blob/main/Self\%20Data\%20Report.ipynb}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Time Series $\textbf{\&}$ Forecasting Analysis}{\em Summer 2021}{Monthly Gas Production Analysis}{}
\item Processed time series data which include non-stationary and seasonality and proceeded transformation methods and differencing to remove its seasonality and non stationarity. 
\item Constructed visualizations of the transformed data and obtained potential parameters for SARIMA model.
\item Performed diagnostic checking for time series data's residuals including properties resembling White Noise and compared AICc values to determine best SARIMA model.
\item Generated forecasting data while compare original data to infer overall analysis. 
\item $\textbf{Link:}$ \url{https://github.com/ohayosua/Projects/blob/main/TIME-SERIES-ANALYSIS-GAS.pdf}
\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{\bf University of California, Santa Barbara}{\em September 2018 - June 2021}{Bachelor of Arts in Statistics \& Data Science / Bachelor of Arts in Economics}{}
\item Relevant Coursework: Time Series, Principles of Data Science with R, Introduction to Statistical Machine Learning, Regression Analysis, Statistical Data Science, Probability and Statistics
\end{rSubsection}

\end{rSection}
%------------------------------------------------


\begin{rSection}{Experience}

\begin{rSubsection}{UCSB Arts $\&$ Lectures}{\em June 2020 -  September 2020}{Online Student Ambassador/Web Designer}{Santa Barbara, CA}
\item Constructed templates for UCSB A$\&$L website created for an online focus towards student content centered around arts and ideas. 
\item Designed potential layout for official website pages while generating content for weekly emails and developed weekly digital content.
\item Collaborated with project teams to filter/input archives into the website and consistently update events, blogs, playlists, and data associated with A$\&$L from existing Excel data set.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
